Nonlinear Dendritic Coincidence Detection for Supervised Learning

### 2021-04-20 notes/draft_article.tex
.

		The resulting accuracy as a function of $N_{dist}$ and $s$
		is shown in Fig.~\ref{fig:classification_accuracy}.
		Albeit differences are small, the compartment model does
		show a better overall accuracy for the tested parameter range.

@@

		However, for our compartment model, we chose to explicitly set the
		threshold to be the mean value between the high- and low-activity regime
		in our compartment model, i.e.\ $\theta_M = (1+\alpha)/2$. By doing so, LTP is
		preferably induced if both basal and apical input are present at the same
		time. Furthermore, instead of the weight decay term, we chose to keep
		the weight normalization as introduced in \eqref{eq:weight_norm}.
		Obviously, for the point model, the reasoning behind our choice of
		$\theta_M$ did not apply. Still, to provide some level of comparability,
		we also ran simulations with a point model where the sliding threshold was
		calculated as a running average of $y^2$. Furthermore, we did not use
		weight normalization in this case, but chose to use a small weight decay term
		with $\epsilon = 0.1$. The results are shown in 
		Fig.~\ref{fig:classification_accuracy_bcm} (classification task) and 
		Fig.~\ref{fig:classification_accuracy_bcm} (Basal-Apical alignment). 
		While the accuracy of the classification for the point model
		is at most comparable to Hebbian learning, the BCM-like rule for the 
		compartment model significantly increases the accuracy for the tested
		parameter range (compare Fig.~\ref{fig:classification_accuracy}).

		Likewise, the compartment model significantly benefits from
		the BCM rule in terms of basal-apical alignment, while only marginal
		improvements can be observed for the point model
		(compare Fig.~\ref{fig:corr_dimension_scaling_bcm} 
		with Fig.~\ref{fig:corr_dimension_scaling}).

@@

>>>>

		The resulting accuracy as a function of $N_{dist}$ and $s$
		is shown in Fig.~\ref{fig:classification_accuracy}.
		Albeit differences are small, the compartment model does
		show a better overall accuracy for the tested parameter range.
		It should be noted, though, that the advantage of the compartment
		model becomes even less prominent when looking at the actual
		correlation between proximal and distal input as a
		measure of successful learning (as done in the previous section).
		Fig.~\ref{fig:classification_correlation} in the supplementary 
		section shows that the compartment model allows for a marginally
		larger scaling among the distraction dimensions.

@@

		However, for our compartment model, we chose to explicitly set the
		threshold to be the mean value between the high- and low-activity regime
		in our compartment model, i.e.\ $\theta_M = (1+\alpha)/2$. By doing so, LTP is
		preferably induced if both basal and apical input are present at the same
		time. Furthermore, instead of the weight decay term, we chose to keep
		the weight normalization as introduced in \eqref{eq:weight_norm}.
		Obviously, for the point model, the reasoning behind our choice of
		$\theta_M$ did not apply. Still, to provide some level of comparability,
		we also ran simulations with a point model where the sliding threshold was
		calculated as a running average of $y^2$. Furthermore, we did not use
		weight normalization in this case, but chose to use a small weight decay term
		with $\epsilon = 0.1$. The results are shown in 
		Fig.~\ref{fig:classification_accuracy_bcm} (classification task) and 
		Fig.~\ref{fig:classification_accuracy_bcm} (Basal-Apical alignment). 
		While the accuracy of the classification for the point model
		is at most comparable to Hebbian learning, the BCM-like rule for the 
		compartment model significantly increases the accuracy for the tested
		parameter range (compare Fig.~\ref{fig:classification_accuracy}). 
		Still, as for the Hebbian learning rule, this result should be taken
		with a grain of salt, as Fig.~\ref{fig:classification_correlation_bcm}
		in the supplementary section indicates that a rather large part of 
		the region ($s>5$) showing good
		classification performance for the compartment model in 
		Fig.~\ref{fig:classification_accuracy_bcm} does hardly exhibit any actual
		correlation between proximal and distal input, making it likely that
		the accuracy of the classification could be easily impaired in this regime, 
		e.g.\ by injecting small amounts of noise.

		The compartment model also significantly benefits from
		the BCM rule in terms of basal-apical alignment as tested in Sect.~\ref{sect:alignment}, 
		while only marginal
		improvements can be observed for the point model
		(compare Fig.~\ref{fig:corr_dimension_scaling_bcm} 
		with Fig.~\ref{fig:corr_dimension_scaling}).

@@

		\section{Supplementary Material}
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\begin{figure}
			\includegraphics[width=\columnwidth]{classification_correlation_dimension_scaling}
			\caption{{\bf Alignment between Basal and Apical Input after Binary Classification Learning.}
				Correlation between proximal and distal Input after training as described in 
				Sect.~\ref{sect:classification}.}
			\label{fig:classification_correlation}
		\end{figure}
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\begin{figure}
			\includegraphics[width=\columnwidth]{classification_correlation_dimension_scaling_bcm}
			\caption{{\bf Alignment between Basal and Apical Input after Binary Classification Learning
					using a BCM-like Rule.}
				Correlation between proximal and distal Input after linear classification 
				training as described in Sect.~\ref{sect:classification}, but using the plasticity
				rules given in Sect.~\ref{sect:non-hebbian}.}
			\label{fig:classification_correlation_bcm}
		\end{figure}
		%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
